Sound Automated Synthesis of Digital Controllers

### 2016-10-13 paper/paper.tex
removed duplicated paragraph + todo
Fixed cline in experiments table.

Let $\tilde C(z)$ and $\tilde G(z)$ be the transfer functions represented
using Fixed-Point bit vectors with integer size $I_b$ and fractional
size $F_b$, whose domain is $\mathbb{R}\langle I_b,F_b \rangle \supseteq \mathbb{R}\langle I,F \rangle$.
%
\begin{align}
\small
\label{digital_controller_plant_tf}
\tilde C(z)&=\frac{\tilde \beta_{0}+\tilde \beta_{1}z^{-1}+...+\tilde \beta_{M_C}z^{-M_C}}{\tilde \alpha_{0}+\tilde \alpha_{1}z^{-1}+...+\tilde \alpha_{N_C}z^{-N_C}}, \\
%\label{plant_tf}
\tilde G(z)&=\frac{\tilde b_{0}+\tilde b_{1}z^{-1}+...+\tilde b_{M_G}z^{-M_G}}{\tilde a_{0}+\tilde a_{1}z^{-1}+...+\tilde a_{N_G}z^{-N_G}}.
\end{align}

Since the controller is synthesized in the $\mathbb{R}\langle I,F \rangle$
domain,
%
 $$\forall i \leq N_C, j \leq M_C\ \  \tilde \beta_{i} \equiv \beta_{i} \wedge \tilde \alpha_{j} \equiv \alpha_{j} \Leftrightarrow \tilde C(z) \equiv C(z)$$

Two approaches have been taken to synthesise a stable controller based on this model.
The first uses interval arithmetic, representing the coefficients $[{c}_i-\Delta_p{c}_i-\Delta_b{c}_i\ ,\ {c}_i+\Delta_p{c}_i-\Delta_b{c}_i+(2^{-F_b})]$  
and rounding operations outwards during the process. This results in a tighter calculation of the error at the cost of performance.

@@

There are two approaches for the {\sc verify} phase based on the
described model.  The first uses interval arithmetic, representing the
coefficients
$[{c}_i-\Delta_p{c}_i-\Delta_b{c}_i\ ,\
{c}_i+\Delta_p{c}_i-\Delta_b{c}_i+(2^{-F_b})]$
and rounding operations outwards during the process. 
% This results in a
% tighter calculation of the error at the cost of
% performance.
Synthesised controllers using this verifier will always
be correct and only generate counterexamples when the precision of the
engine is insuficient.  Given the high computational cost of this
approach, we also designed a second approach, which we describe below.
In our experimental section Sec.~\ref{sec:experiments}, we 
show that the increase in speed of the second approach 
over the first one is in most cases of several orders of magnitude.

@@

%$$
%\begin{array}{ll}
%N_C(z) {=} 0z^2{+}0z{+}0\\
%D_C(z) {=} 0z^2{+}0z{+}0\\
%\end{array}
%$$
$$
\blue{
C(z)=\frac{0z^2{+}0z{+}0}{0z^2{+}0z{+}0}
}
$$

@@

\begin{table}[H]
\centering
\begin{tabular}{c l | r l}
      & Benchmark                  & Base    & \\\cline{1-2}
$G_1$ & CruiseControl02            & 17\,s   & \\
$G_1$ & CruiseControl02$^\dagger$  & 46\,s   & \\
$G_2$ & SpringMassDamper           & 28\,s   & \\
$G_2$ & SpringMassDamper$^\dagger$ & \xmark  & \\
$G_2$ & SatelliteB2                & 7\,s    & \\
$G_2$ & SatelliteB2$^\dagger$      & 6601\,s & \tbmark\\
$G_2$ & SatelliteC2                & 2\,s    & \\
$G_2$ & SatelliteC2$^\dagger$      & 76\,s   & \tbmark\\
      & a\_PL1\_SCH2\_IMPL1        & 2704\,s & \\
      & a\_PL1\_SCH2\_IMPL2        & 538\,s  & \\
      & a\_PL1\_SCH2\_IMPL3        & 12\,s   & \\
      & a\_PL1\_SCH3\_IMPL1        & 318\,s  & \\
      & a\_PL1\_SCH3\_IMPL2        & 967\,s  & \\
      & a\_PL1\_SCH3\_IMPL3        & 9798\,s & \\
      & a\_PL1\_SCH4\_IMPL1        & 6304\,s & \\
\end{tabular}

>>>>

% Let $\tilde C(z)$ and $\tilde G(z)$ be the transfer functions represented
% using Fixed-Point bit vectors with integer size $I_b$ and fractional
% size $F_b$, whose domain is $\mathbb{R}\langle I_b,F_b \rangle \supseteq \mathbb{R}\langle I,F \rangle$.
% %
% \begin{align}
% \small
% \label{digital_controller_plant_tf}
% \tilde C(z)&=\frac{\tilde \beta_{0}+\tilde \beta_{1}z^{-1}+...+\tilde \beta_{M_C}z^{-M_C}}{\tilde \alpha_{0}+\tilde \alpha_{1}z^{-1}+...+\tilde \alpha_{N_C}z^{-N_C}}, \\
% %\label{plant_tf}
% \tilde G(z)&=\frac{\tilde b_{0}+\tilde b_{1}z^{-1}+...+\tilde b_{M_G}z^{-M_G}}{\tilde a_{0}+\tilde a_{1}z^{-1}+...+\tilde a_{N_G}z^{-N_G}}.
% \end{align}

% Since the controller is synthesized in the $\mathbb{R}\langle I,F \rangle$
% domain,
% %
%  $$\forall i \leq N_C, j \leq M_C\ \  \tilde \beta_{i} \equiv \beta_{i} \wedge \tilde \alpha_{j} \equiv \alpha_{j} \Leftrightarrow \tilde C(z) \equiv C(z)$$

% Two approaches have been taken to synthesise a stable controller based on this model.
% The first uses interval arithmetic, representing the coefficients $[{c}_i-\Delta_p{c}_i-\Delta_b{c}_i\ ,\ {c}_i+\Delta_p{c}_i-\Delta_b{c}_i+(2^{-F_b})]$

% \cdsay{Dario, what coefficients are these?}

% and rounding operations outwards during the process. This results in a tighter calculation of the error at the cost of performance.

@@

There are two approaches for the {\sc verify} phase based on the
described model.  The first uses interval arithmetic, representing the
coefficients
$[{c}_i-\Delta_p{c}_i-\Delta_b{c}_i\ ,\
{c}_i+\Delta_p{c}_i-\Delta_b{c}_i+(2^{-F_b})]$
and rounding operations outwards during the process. 
\cdsay{dario, what coefficients are these?}
% This results in a
% tighter calculation of the error at the cost of
% performance.
Synthesised controllers using this verifier will always
be correct and only generate counterexamples when the precision of the
engine is insuficient.  Given the high computational cost of this
approach, we also designed a second approach, which we describe below.
In our experimental section Sec.~\ref{sec:experiments}, we 
show that the increase in speed of the second approach 
over the first one is in most cases of several orders of magnitude.

@@

%$$
%\begin{array}{ll}
%N_C(z) {=} 0z^2{+}0z{+}0\\
%D_C(z) {=} 0z^2{+}0z{+}0\\
%\end{array}
%$$
$$
C(z)=\frac{0z^2{+}0z{+}0}{0z^2{+}0z{+}0}
$$

@@

\begin{table}[H]
\centering
\begin{tabular}{c l | r l}
Plant & Benchmark                  & Time    & \\\cline{1-3}
$G_1$ & CruiseControl02            & 17\,s   & \\
$G_1$ & CruiseControl02$^\dagger$  & 46\,s   & \\
$G_2$ & SpringMassDamper           & 28\,s   & \\
$G_2$ & SpringMassDamper$^\dagger$ & \xmark  & \\
$G_2$ & SatelliteB2                & 7\,s    & \\
$G_2$ & SatelliteB2$^\dagger$      & 6601\,s & \tbmark\\
$G_2$ & SatelliteC2                & 2\,s    & \\
$G_2$ & SatelliteC2$^\dagger$      & 76\,s   & \tbmark\\
      & a\_PL1\_SCH2\_IMPL1        & 2704\,s & \\
      & a\_PL1\_SCH2\_IMPL2        & 538\,s  & \\
      & a\_PL1\_SCH2\_IMPL3        & 12\,s   & \\
      & a\_PL1\_SCH3\_IMPL1        & 318\,s  & \\
      & a\_PL1\_SCH3\_IMPL2        & 967\,s  & \\
      & a\_PL1\_SCH3\_IMPL3        & 9798\,s & \\
      & a\_PL1\_SCH4\_IMPL1        & 6304\,s & \\
\end{tabular}
